Who does big team science?

### 2023-12-06 manuscript_scopus.Rmd
fully anon

This manuscript was preregistered with the same conceptual ideas using
Google Scholar and ORC-ID databases (<https://osf.io/f2dtr/?view_only=66e5608437994f288d03a7c8163c0c8c>) but then
was updated with access to the Scopus database for a broader picture of
BTS projects (<https://osf.io/fheun/?view_only=f563879af9e942f7bc49bac937fd3048>). All materials and code can be
found on our OSF page: <https://osf.io/cgx6u/?view_only=7ea2adf9ea7c4995af0d60dde795db6d> or corresponding GitHub
archive: ANONYMIZED.

>>>>

This manuscript was preregistered with the same conceptual ideas using
Google Scholar and ORC-ID databases (MASKED FOR REVIEW^[Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal]) but then
was updated with access to the Scopus database for a broader picture of
BTS projects (MASKED FOR REVIEW). All materials and code can be
found on our OSF page: MASKED FOR REVIEW or corresponding GitHub
archive: MASKED FOR REVIEW.

### 2023-12-06 manuscript_scopus.tex
fully anon

This manuscript was preregistered with the same conceptual ideas using
Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr/?view_only=66e5608437994f288d03a7c8163c0c8c}) but then
was updated with access to the Scopus database for a broader picture of
BTS projects (\url{https://osf.io/fheun/?view_only=f563879af9e942f7bc49bac937fd3048}). All materials and code can be
found on our OSF page: \url{https://osf.io/cgx6u/?view_only=7ea2adf9ea7c4995af0d60dde795db6d} or corresponding GitHub
archive: ANONYMIZED.

>>>>

This manuscript was preregistered with the same conceptual ideas using
Google Scholar and ORC-ID databases (MASKED FOR REVIEW\footnote{Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal}) but then
was updated with access to the Scopus database for a broader picture of
BTS projects (MASKED FOR REVIEW). All materials and code can be
found on our OSF page: MASKED FOR REVIEW or corresponding GitHub
archive: MASKED FOR REVIEW.
